---
title: "counterbalancing_check"
author: "Gal"
date: "7/19/2021"
output: html_document
---

# This RMarkdown is to come up with a counterbalancing scheme for pokebaby-infant Exp2 that balances the distribution of std/dev, fam_duration, and complex and simple

```{r setup, include=FALSE}
library(tidyverse)
library(crossdes)
```


# We do 8 blocks, with either 3/5, 5/7 or 3/7 fam duration and complexity within subjects. Let's simulate 60 subjects, i.e. 20 per fam duration
```{r}
total_subject_number = 60
block_number_per_subj = 8

fam_duration_conditions = 1:3
subjects_per_fam_duration = 20

fam_durations = c(3,5,7)
block_type = c("Std", "Dev")
complexity = c("Simple", "Complex")


indices = c(1,2,2,1,2,1,2,1)

block_type_in_exp = block_type[indices]
complexity_in_exp = complexity[indices]


# preallocate
subject_id = rep(1:total_subject_number, each = block_number_per_subj)
block_number = rep(1:block_number_per_subj, total_subject_number)
counterbalancing_condition = rep(NA, 1, total_subject_number*block_number_per_subj)
block_type = rep(NA, 1, total_subject_number*block_number_per_subj)
fam_duration = rep(NA, 1, total_subject_number*block_number_per_subj)
fam_duration_condition = rep(NA, 1, total_subject_number*block_number_per_subj)
complexity = rep(NA, 1, total_subject_number*block_number_per_subj)
# coun


subject_counter = 1

for (i in fam_duration_conditions) {
  
  
  if (i == 1) {
      current_fam_durations = fam_durations[c(1, 2)]
  }
  else if (i == 2) {
      current_fam_durations = fam_durations[c(2, 3)]
  }
  else if (i == 3) {
      current_fam_durations = fam_durations[c(1, 3)]
  }
  
   # store fam_duration condition
 fam_duration_condition[(1+(i-1)*subjects_per_fam_duration*block_number_per_subj):
                        (subjects_per_fam_duration*block_number_per_subj+(i-1)*subjects_per_fam_duration*block_number_per_subj)] = 
   paste(current_fam_durations, collapse="")
 
  
  # set up rotation matrix
  counterbalancing_matrix = williams(block_number_per_subj)
  
  # set up sampling indices 
 sampling_indices = c(rep(1:block_number_per_subj, floor(subjects_per_fam_duration / block_number_per_subj)), # first repeat 1:8 , 
        sample(1:block_number_per_subj, subjects_per_fam_duration %% block_number_per_subj))  #and then randomly sample the remaining ones
 
 # add to counterbalancing condition
 counterbalancing_condition[(1+(i-1)*subjects_per_fam_duration*block_number_per_subj):
                        (subjects_per_fam_duration*block_number_per_subj+(i-1)*subjects_per_fam_duration*block_number_per_subj)] = as.vector(t(counterbalancing_matrix[sampling_indices, ]))  # index and flatten

}

# initialize df with the things we already have
subject_df = tibble(fam_duration_condition = fam_duration_condition,
                    counterbalancing_condition = counterbalancing_condition,
                    subject_id = subject_id,
                    block_number = block_number)

# now add the things that are based on counterbalnacing condition
subject_df <- subject_df %>% 
  mutate(
    block_type = case_when(
    counterbalancing_condition %% 2 == 1 ~ "Std", # odd is standard 
    counterbalancing_condition %% 2 == 0 ~ "Dev" # odd is standard 
    ),
    complexity = case_when(
      counterbalancing_condition <= block_number_per_subj/2 ~ 'simple',
      TRUE ~ 'complex'
    ),
    fam_duration = case_when(
            counterbalancing_condition <= 2 ~ substr(fam_duration_condition,1,1),
            counterbalancing_condition <= 4 ~ substr(fam_duration_condition,2,2),
            counterbalancing_condition <= 6 ~ substr(fam_duration_condition,1,1),
            counterbalancing_condition <= 8 ~ substr(fam_duration_condition,2,2)
    )
  )

# check out distribution of trials

subject_df %>% dplyr::group_by(block_number, block_type, fam_duration, complexity) %>% 
  dplyr::summarize(n_trial = n()) %>% ggplot(aes(x=block_number, y=n_trial, group=block_type, color = block_type)) + geom_point(alpha=.8, position = position_dodge(width = .1))  + 
  geom_line() + facet_wrap(complexity~fam_duration)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
