```{r}
library(tidyverse)
library(here)

d_1 <- read_csv(here("prepping_followup/participant_tracking_wave1.csv"))
d_2 <- read_csv(here("prepping_followup/participant_tracking_wave2.csv"))
d_3 <- read_csv(here("prepping_followup/participant_tracking_wave3.csv"))

p <- read_csv(here("prepping_followup/participated_0511.csv"))
```


Dear participant, 

We just want to follow-up on our previous message. We would love to have you participate in the study "Look at cute animations and tell us what you think!", which is a follow-up on the study you participated last September. You have already been added to our allow-list. The study should take less than 10 minutes and you will receive $2 as compensation. 

Please don't hesitate to reach out if you have any question! 

Best, 
Anjie Cao 
PhD student at Language and Cognition Lab 
Stanford University 

```{r}
follow_up <- bind_rows(d_1, d_2, d_3) %>% 
  filter(!(prolific_id %in% p$participant_id)) 

write_csv(follow_up, here("prepping_followup/followup_0511.csv"))
```

