---
title: "RT_plotting"
author: "anjie & gal"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(ggiraphExtra)
library(plotrix)
```

# Load data
```{r}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))

```
# Descriptive 
```{r}
RT_data %>% 
  distinct(subject) %>% 
  count()
```

# Raw data {.tabset}
 
## overall 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() 
```

## by trial type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_type)
```

## by trial complexity 
```{r}
RT_data %>% 
  ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_complexity)
```

## by block type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~block_type)
```

## by item id 
### simple 
```{r}
RT_data %>% 
  filter(trial_complexity == "simple") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

### complex 
```{r}
RT_data %>% 
  filter(trial_complexity == "complex") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```



# Basic plotting of RT data

pruning: 

rt_summary <- df.rt_trimmed %>% 
  summarise(
    median = median(log(rt)),
    mad = mad(log(rt)), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad)
  
df.rt_trimmed <- df.rt_trimmed %>% 
  filter(!(log(rt) > rt_summary$upper | log(rt) < rt_summary$lower))

```{r}


# before exclusion
summarized <- RT_data %>%
group_by(trial_number, item_type, trial_complexity) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(rt), Std=sd(rt), SE = std.error(rt), n = n())



ggplot(summarized, aes(x=trial_number, y=medianRT, colour=item_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(~trial_complexity)

```

