---
title: "00_preprocessing.rmd"
author: "anjie"
date: "9/2/2021"
output: html_document
---
```{r}
library(tidyverse)
library(here)
library(jsonlite)
library(stringr)


source(here("helper/tidy_rt_task_data.r"))

d <- read.csv(here("data/lol.csv")) %>% filter(prolific_id != "") %>% 
  distinct(prolific_id, trial_index, .keep_all = TRUE)

# get rid of the incompplete files 

incomplete_prolific_id <- d %>% 
  group_by(prolific_id) %>% 
  count() %>% 
  filter(n < 100) %>% 
  pull(prolific_id)

d <- d %>% filter(!prolific_id %in% incomplete_prolific_id)

```


# extract looking time data 

```{r}
# looking time
lt_d <- d %>% 
  filter(trial_type == "curtain-display") %>% 
  filter(!is.na(background_type) & background_type != "") %>% 
  select(prolific_id, trial_type, total_rt, block_type, 
         background_stimulus, deviant_stimulus, background_type, deviant_type, violation_type, 
         trial_number) %>% 
  select(-trial_type) %>% 
  rename(total_trial_number = trial_number) %>% 
  group_by(prolific_id, background_stimulus, deviant_stimulus) %>% 
  mutate(trial_number = row_number()) %>% 
  left_join(
    d %>% filter(trial_type == "curtain-display") %>%
  filter(!is.na(background_type) & background_type != "") %>% distinct(prolific_id, background_stimulus, deviant_stimulus) %>% 
    group_by(prolific_id) %>% mutate(block_number = row_number()), 
  by = c("prolific_id", "background_stimulus", "deviant_stimulus")
  ) %>% 
  mutate(
    animacy = case_when(
    grepl("inanimate", background_type) ~ "inanimate", 
    TRUE ~ "animate"), 
    
    number = case_when(
    grepl("single", background_type) ~ "single", 
    TRUE ~ "pair"
  ),
  
    pose = case_when(
    grepl("left", background_type) ~ "left", 
    TRUE ~ "right"
  ),
  
    trial_type = case_when(
      (block_type == "deviant_block" &trial_number == total_trial_number) ~ "deviant", 
      TRUE ~ "background"
    )
  
    ) %>% 
  filter(!is.na(total_trial_number))

lt_d <- lt_d %>% 
  mutate(
    background_id = str_extract_all(background_stimulus, "\\d+")[[1]], 
    background_animacy = ifelse(grepl("inanimate", background_stimulus), "inanimate", "animate"), 
    background_pose = ifelse(grepl("left", background_stimulus), "left", "right"), 
    background_number = ifelse(grepl("pair", background_type), "pair", "single"), 
    deviant_id = ifelse(grepl("null", deviant_stimulus), "NA", 
                        str_extract_all(deviant_stimulus, "\\d+")[[1]]), 
    deviant_animacy = ifelse(grepl("inanimate", deviant_stimulus), "inanimate", "animate"), 
    deviant_pose = ifelse(grepl("left", deviant_stimulus), "left", "right"), 
    deviant_number = ifelse(grepl("pair", deviant_type), "pair", "single"), 
  ) %>% 
  mutate(
    same_animacy = (background_animacy == deviant_animacy), 
    same_number = (background_number == deviant_number), 
    same_pose = (background_pose == deviant_pose),
    same_id = (background_id == deviant_id)
  ) %>% 
  mutate(
    violation_type = case_when(
      # animacy violation
      same_animacy == FALSE & same_number == TRUE & same_pose == TRUE  ~ "animacy", 
      # pose violation 
      same_animacy == TRUE & same_number == TRUE & same_pose == FALSE & same_id == TRUE ~ "pose", 
      # identity violation 
      same_animacy == TRUE & same_number == TRUE & same_pose == TRUE & same_id == FALSE ~ "identity", 
      # number violation
      same_animacy == TRUE & same_number == FALSE & same_pose == TRUE & same_id == TRUE ~ "number", 
      block_type == "background_block" ~ "background", 
      TRUE ~ "error!"
    )
  )
  
  

```

# extract curiosity rating data

```{r}
# curiosity rating 
curiosity_rating_df <- d %>% 
  filter(trial_type == "survey-likert") %>% 
  filter(rating_type != "") %>% 
  select(prolific_id, rating_type, response) %>% 
  mutate(response = gsub("'", "\"", response)) %>% 
  mutate(curiosity_rating = map(response, ~ fromJSON(.) %>% as.data.frame()) %>% unlist()) %>% 
  select(-response) %>% 
  group_by(prolific_id) %>% 
  mutate(block_number = row_number()) %>% 
  left_join(lt_d %>% ungroup() %>%  distinct(prolific_id, background_type, deviant_type, block_number) %>% 
              select(prolific_id, background_type, deviant_type, block_number), by = c("prolific_id", "block_number")) %>% 
  mutate(rating_stimus_type = case_when(
    rating_type == "background" ~ background_type, 
    rating_type == "deviant" ~ deviant_type
  )) %>% 
  mutate(
    animacy = case_when(
    grepl("inanimate", background_type) ~ "inanimate", 
    TRUE ~ "animate"), 
    
    number = case_when(
    grepl("single", background_type) ~ "single", 
    TRUE ~ "pair"
  ),
  
    pose = case_when(
    grepl("left", background_type) ~ "left", 
    TRUE ~ "right"
  )
    ) %>% 
  select(prolific_id, rating_type, curiosity_rating, block_number, rating_stimus_type, animacy, number, pose)



```


# extract complexity & similarity rating data 

```{r}
c_s_ratings <- d %>% 
  filter(trial_type == "survey-likert") %>% 
  filter(rating_type == "") %>% 
  select(prolific_id, violation_type, similarity_rating_background, similarity_rating_deviant, similarity_rating_violation, complexity_rating_type, complexity_rating_stimulus, response) %>% 
  mutate(rating_type = 
           case_when(
    complexity_rating_type == "" ~ "similarity_rating", 
    similarity_rating_violation == "" ~ "complexity_rating"
  )) %>% 
   mutate(response = gsub("'", "\"", response)) %>% 
  mutate(rating = map(response, ~ fromJSON(.) %>% as.data.frame()) %>% unlist()) %>% 
  select(-response) 

  
```


# sneak peak of the raw looking time data 

```{r}
lt_d %>% 
  ggplot(aes(x = trial_number, y = total_rt, color = trial_type)) + 
  stat_summary(fun.data = "mean_cl_boot")+
  facet_wrap(~total_trial_number)

lt_d %>% 
  filter(trial_type == "deviant") %>% 
  ggplot(aes(x = violation_type, y = total_rt)) + 
  stat_summary(fun.data = "mean_cl_boot")
  


```

```{r}
lt_d %>% write_csv(here("data/pilot_look.csv"))
```





# exclusion 

## Participant-based exclusion:

We exclude participants if either 
(a) the standard deviation of log-transformed of their reaction times on all trials is less than 0.15 
```{r}
low_var_in_sbj <- lt_d %>% 
  ungroup() %>% 
  group_by(prolific_id) %>% 
  summarise(mean_rt = mean(total_rt), 
            sd = sd(total_rt)) %>% 
  filter(sd < 0.15) %>% 
  pull(prolific_id)

low_var_in_sbj

df_low_var <- tibble("exclude_reason" = rep("low_var", length(low_var_in_sbj)), 
                     sbj = low_var_in_sbj)
```

(b) spent more than three absolute deviations away from the medians of the task completion time as reported by Prolific.


```{r}
p_df <- read_csv(here("data/prolific.csv")) %>% 
  janitor::clean_names()

p_summary <- p_df %>% 
  select(participant_id, time_taken) %>% 
   summarise(
     median = median(time_taken, na.rm = TRUE),
    mad = mad(time_taken, na.rm = TRUE), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad) 

p_id <- p_df %>% 
  filter(time_taken > p_summary$upper | time_taken < p_summary$lower) %>% 
  select(participant_id) %>% 
  pull()


df_prolific <- tibble("exclude_reason" = rep("prolific", length(p_id)), 
                     sbj = p_id)
```

(c) provided the same response to 80% the complexity rating task 

```{r}
same_ratings <- c_s_ratings %>% 
  filter(rating_type == "complexity_rating") %>% 
  group_by(prolific_id) %>% 
  count() %>% 
  rename(total_n = n) %>% 
  left_join(
    
    c_s_ratings %>% 
  filter(rating_type == "complexity_rating") %>% 
  group_by(prolific_id, rating) %>% 
  count(), by = c("prolific_id") ) %>% 
  filter(
    n / total_n > .8
  )


df_same_ratings <- tibble("exclude_reason" = rep("same_rating", length(same_ratings$prolific_id)), 
                     sbj = same_ratings$prolific_id)

```





all excluded subject 

```{r}

participants_exclusion <- bind_rows(df_low_var, df_prolific, df_same_ratings)
write_csv(participants_exclusion, here("data/p_level_exclusion.csv"))

participants_exclusion <- read_csv(here("data/p_level_exclusion.csv"))


```


```{r}

trimmed_lt_d <- lt_d %>% 
  filter(!(prolific_id %in% participants_exclusion$sbj))

trimmed_curiosity_rating_df <- curiosity_rating_df %>% 
  filter(!(prolific_id %in% participants_exclusion$sbj))

trimmed_c_s_rating_df <- c_s_ratings %>% 
  filter(!(prolific_id %in% participants_exclusion$sbj))


```


## Trial based exclusion:
We exclude a trial if it is three absolute deviations away from the median in the log-transformed space across all participants.

```{r}

rt_summary <- lt_d %>% 
  ungroup() %>% 
  summarise(
    median = median(log(total_rt)),
    mad = mad(log(total_rt)), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad)
  
final_trimmed_lt_d <- trimmed_lt_d %>% 
  filter(!(log(total_rt) > rt_summary$upper | log(total_rt) < rt_summary$lower))

```

# Add embedding distance into the mix

```{r}
em_dis <- read_csv(here("data/eucledian_distances_with_number.csv")) %>% rename(stim_name = `...1`)
replace_name <- function(x) gsub("media/padded_stims/", "", x)
final_trimmed_lt_d <- final_trimmed_lt_d %>% 
  mutate_at(c("background_stimulus", "deviant_stimulus"), replace_name) %>% 
  mutate_at(c("background_stimulus", "deviant_stimulus"),
    funs(case_when(
      number == "single" ~ ., 
      TRUE ~ gsub("(.*)(\\.)", paste0("\\1_pair\\2"), .)
    )))


get_distance <- function(stim_a_name, stim_b_name,  dist){
  if (stim_a_name  == "" | stim_b_name  == ""){
    return (tibble("val" = NA_real_))
  }else{
    return( 
      tibble("val" = dist %>%
      filter(stim_name == {{stim_b_name}}) %>% 
      select({{stim_a_name}}) %>% 
      pull())
      )
  }
  
}

final_trimmed_lt_d <- final_trimmed_lt_d %>% 
  ungroup() %>% 
  mutate(edist = map2_df(.x = final_trimmed_lt_d$background_stimulus, 
                        .y = final_trimmed_lt_d$deviant_stimulus, 
                        .f = get_distance, em_dis)) %>% 
  unnest(edist)
```




# write out all the data 


```{r}
write_csv(final_trimmed_lt_d, here("data/01_trimmed_data/trimmed_lt_d.csv"))
write_csv(trimmed_curiosity_rating_df, here("data/01_trimmed_data/trimmed_curiosity_rating.csv"))
write_csv(trimmed_c_s_rating_df, here("data/01_trimmed_data/trimmed_cs_rating.csv"))

```





