---
title: "00_preprocessing.rmd"
author: "anjie"
date: "9/2/2021"
output: html_document
---
```{r}
library(tidyverse)
library(here)
library(jsonlite)

source(here("helper/tidy_rt_task_data.r"))

```

# set up paths 
```{r}

MERGED_DATA_PATH <- here("data/merged_data.csv")
d <- read_csv(MERGED_DATA_PATH)

```

```{r}
# looking time
lt_d <- d %>% 
  filter(trial_type == "curtain-display") %>% 
  filter(!is.na(background_type)) %>% 
  select(subject, trial_type, total_rt, block_type, 
         background_stimulus, deviant_stimulus, background_type, deviant_type, violation_type, 
         trial_number) %>% 
  select(-trial_type)

# curiosity rating 
curiosity_rating_df <- d %>% 
  filter(trial_type == "survey-likert") %>% 
  filter(!is.na(rating_type)) %>% 
  select(subject, rating_type, response) %>% 
  mutate(curiosity_rating = map(response, ~ fromJSON(.) %>% as.data.frame()) %>% unlist()) %>% 
  select(-response) %>% 
  group_by(subject) %>% 
  mutate(block_number = row_number(), 
         rating_type = "curiosity") 
  
# complexity rating 
# lol missing some important informaiton i guess? 
complexity_rating_df <- d %>% 
  filter(trial_type == "survey-likert") %>% 
  filter(!is.na(complexity_rating_type)) %>% 
  select(subject, rating_type, response, complexity_rating_type, complexity_rating_stimulus) %>% 
  mutate(complexity_rating = map(response, ~ fromJSON(.) %>% as.data.frame()) %>% unlist()) %>% 
  select(-response) %>% 
  mutate(rating_type = "complexity") 

# similarity rating 
similarity_rating_df <- d %>% 
  filter(trial_type == "survey-likert") %>% 
  filter(!is.na(similarity_rating_violation)) %>% 
  select(subject, response, similarity_rating_background, similarity_rating_deviant, similarity_rating_violation) %>% 
  mutate(complexity_rating = map(response, ~ fromJSON(.) %>% as.data.frame()) %>% unlist()) %>% 
  select(-response) %>% 
  mutate(rating_type = "similarity") 



```



# exclusion 

## Participant-based exclusion:

We exclude participants if either 
(a) the standard deviation of log-transformed of their reaction times on all trials is less than 0.15 
```{r}
low_var_in_sbj <- lt_d %>% 
  group_by(subject) %>% 
  summarise(mean_rt = mean(total_rt), 
            sd = sd(total_rt)) %>% 
  filter(sd < 0.15) %>% 
  pull(subject)

low_var_in_sbj

df_low_var <- tibble("exclude_reason" = rep("low_var", length(low_var_in_sbj)), 
                     sbj = low_var_in_sbj)
```

(b) spent more than three absolute deviations away from the medians of the task completion time as reported by Prolific.

```{r}
# gather all of the prolific data

MIN_ROW <- 100  #subject to change 

merge_and_deidentify_data <- function(raw_data_directory, 
                                      min_row){
  
  raw_files <- str_c(raw_data_directory, dir(here(raw_data_directory), "*.csv"))
  
  # count how many rows in each file 
  RAW_count <- map_df(raw_files, function(file) {
    d <- read_csv(file) %>% 
      count() %>% 
      mutate(
        file_name = file 
      )
  })   
  
  
  RAW_DATA <- map_df((RAW_count %>% filter(n > min_row))$file_name,
                     function(file){
                       d <- read_csv(file)
                     }) 
  
  
  return (RAW_DATA)
  
}

raw_d <- merge_and_deidentify_data(here("data/00_raw_data/"), MIN_ROW)

```


```{r}
p_df <- read_csv(here("data/prolific.csv")) %>% 
  janitor::clean_names()

p_summary <- p_df %>% 
  select(participant_id, time_taken) %>% 
   summarise(
     median = median(time_taken),
    mad = mad(time_taken), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad) 

p_id <- p_df %>% 
  filter(time_taken > p_summary$upper | time_taken < p_summary$lower) %>% 
  select(participant_id) %>% 
  pull()

p_sbj <- raw_d %>% 
  distinct(subject, prolific_id) %>% 
  filter(prolific_id %in% p_id) %>% 
  pull(subject)
  
p_sbj

df_prolific <- tibble("exclude_reason" = rep("prolific", length(p_sbj)), 
                     sbj = p_sbj)
```



c) in the math question condition and the memory question condition, answer 3 out of 8 questions wrong; or

```{r}


memory_sbj <-  complexity_rating_df %>% 
  group_by(subject) %>% 
  select(subject, complexity_rating) %>% 
  group_by(subject, complexity_rating) %>% 
  count() %>% 
  mutate(ratio = n / 24) %>% 
  filter(ratio >.8) %>% 
  pull(subject)

memory_sbj

df_memory <- tibble("exclude_reason" = rep("memory", length(memory_sbj)), 
                     sbj = memory_sbj)
```



all excluded subject 
```{r}

participants_exclusion <- bind_rows(df_low_var, df_prolific, df_memory)
write_csv(participants_exclusion, here("data/p_level_exclusion.csv"))


exclude_participant <- unique(c(
                               memory_sbj, 
                               p_sbj, 
                               low_var_in_sbj))

```


```{r}

trimmed_lt_d <- lt_d %>% 
  filter(!(subject %in% exclude_participant))

trimmed_curiosity_rating_df <- curiosity_rating_df %>% 
  filter(!(subject %in% exclude_participant))

trimmed_complexity_rating_df <- complexity_rating_df %>% 
  filter(!(subject %in% exclude_participant))

trimmed_similarity_rating_df <- similarity_rating_df %>% 
  filter(!(subject %in% exclude_participant))
```


## Trial based exclusion:
We exclude a trial if it is three absolute deviations away from the median in the log-transformed space across all participants.

```{r}

rt_summary <- lt_d %>% 
  summarise(
    median = median(log(total_rt)),
    mad = mad(log(total_rt)), 
    upper = median + 3 * mad, 
    lower = median - 3 * mad)
  
final_trimmed_lt_d <- trimmed_lt_d %>% 
  filter(!(log(total_rt) > rt_summary$upper | log(total_rt) < rt_summary$lower))

```



# write out all the data 


```{r}
write_csv(final_trimmed_lt_d, here("data/01_trimmed_data/trimmed_lt_d.csv"))
write_csv(trimmed_curiosity_rating_df, here("data/01_trimmed_data/trimmed_curiosity_rating.csv"))
write_csv(trimmed_complexity_rating_df, here("data/01_trimmed_data/trimmed_complexity_rating.csv"))
write_csv(trimmed_similarity_rating_df, here("data/01_trimmed_data/trimmed_similarity_rating_df.csv"))
```



