---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```
We are learning theta, the probability of a single binary feature being active. 


Our training data are individual exemplars of the concept, e.g. sample sfrom theta, y1....yn. 

$$ p(\theta) = Beta(\alpha, \beta) $$

this defines a simple Beta-Bernoulli conjugate model, so 

$$p(y | \theta) = Bernoulli(\theta)$$

but actually we don't observe y directly. for each examplear $$y_i$$, we can choose to gather noisy sample $$z_i1...z_it$$ from these. these samples are: 

\begin{equation}
p(z_{ij} | y_i) = 
\begin{cases}
    \epsilon, & \text{for } y_i = 0 \\
    1-\epsilon, & \text{for } y_i = 1. \\
\end{cases}
\end{equation}

```{r}
# our training data are individual exemplar of this concept y 
y_1 = c(1, 0, 0) 
y_2 = c(1, 0, 0) # is this true? 
y_3 = c(1, 0, 0) 
# or does each individual feature is a theta, and the theta is shared among all features? 
# so it will look something like 
y_1 = c(bernoulli(theta), 
        bernoulli(theta), 
        bernoulli(theta))  
y_2 = c(bernoulli(theta), 
        bernoulli(theta), 
        bernoulli(theta)) 
...

#and something new would look like 
z_1  = c(bernoulli(theta_prime), 
        bernoulli(theta_prime), 
        bernoulli(theta_prime))

```

```{r}
# the first thing looks easier, so i'll go with that one for now
y_1 = c(1)

# theta is prior for y_1
#p_theta = beta(alpha, beta)
p_theta = 0.5 

# what we want is 
# p_theta_given_overbar_z

p_theta_given_overbar_z = (p_overbar_z_given_theta * p_theta) / p_overbar_z
```


```{r}
get_z_i_j_given_theta <- function(i, j, theta, epsilon){
  
  z_i_j_given_y_i_is_one = epsilon # very questionable 
  y_i_is_one_given_theta = theta # bernoulli? 
  
  z_i_j_given_y_i_is_zero = 1- epsilon # very questionable 
  y_i_is_zero_given_theta = 1 - theta
  
  z_ij_given_theta = z_i_j_given_y_i_is_one * y_i_is_one_given_theta + 
    z_i_j_given_y_i_is_zero *y_i_is_zero_given_theta
  
  return (z_ij_given_theta)
}

get_z_overbar_given_theta <- function(i, j, theta, epsilon){
  
  all_z_ij_given_theta <- c() 
  
  for (i_index in seq(1:i)){
    for(j_index in seq(1:j)){
      
      z_ij_given_theta <- get_z_i_j_given_theta(i, j, theta, epsilon)
      
      all_z_ij_given_theta <- c(all_z_ij_given_theta, z_ij_given_theta)
      
    }
  }
  
  z_overbar_given_theta <- prod(all_z_ij_given_theta)
  
  return (z_overbar_given_theta)
}


get_all_z_overbar_given_theta <- function(i, j, epsilon, all_thetas){
  
  all_p_overbar_z_given_theta <- c()
  
  for (theta_i in 1:length(all_thetas)){
    theta = all_thetas[theta_i]
    #print(theta)
    current_z_overbar_given_theta <- get_z_overbar_given_theta(i, j, theta, epsilon)
    all_p_overbar_z_given_theta <- c(all_p_overbar_z_given_theta, current_z_overbar_given_theta)
  
  }
  
  return(all_p_overbar_z_given_theta)
  
}

get_overbar_z <- function(i, j, epsilon, all_thetas){
  
  all_z_overbar_z_given_theta <- get_all_z_overbar_given_theta(i, j, epsilon, all_thetas)
  
  return (sum(all_z_overbar_z_given_theta * all_thetas))
  
}
```

```{r}
n = 1 # one exemplar 
t = 3 # look at for 3 second 
theta = 0.5
overbar_z_given_theta <- get_z_overbar_given_theta(n, t, theta, epsilon)


epsilon = 0.2

all_thetas = c(0.2, 0.4, 0.6, 0.8)

all_p_overbar_z_given_theta <- get_all_z_overbar_given_theta(n, t, epsilon, all_thetas)

overbar_z <- get_overbar_z(n, t, epsilon, all_thetas)

final_distribution <- (all_p_overbar_z_given_theta * all_thetas)/overbar_z

all_thetas
all_p_overbar_z_given_theta
overbar_z
final_distribution

```





```{r}
alpha  = 1
beta = 2
theta <- rbeta(1, 1,  2)
theta
```

```{r}
sample.space <- c(0,1)
theta <- rbeta(1, 1,  2)
theta
N <- 20 # we want to flip a coin 20 times

flips <- sample(sample.space, 
                size = N, 
                replace = TRUE, 
                prob = c(theta, 1 - theta))

flips_rb <- rbinom(n = 1, 
                size = 1, 
                prob = theta)




```

```{r}
get_z_i_j_given_y_i <- function(y_i, epsilon){
  if (y_i == 0){
    return (epsilon)
  }else{
    return (1 - epsilon)
  }
}
```


```{r}
get_z_i_j_given_theta <- function(i, j, theta, epsilon){
  
  z_i_j_given_y_i_is_one = epsilon # very questionable 
  y_i_is_one_given_theta = theta # bernoulli? 
  
  z_i_j_given_y_i_is_zero = 1- epsilon # very questionable 
  y_i_is_zero_given_theta = 1 - theta
  
  z_ij_given_theta = z_i_j_given_y_i_is_one * y_i_is_one_given_theta + 
    z_i_j_given_y_i_is_zero *y_i_is_zero_given_theta
  
  return (z_ij_given_theta)
}
```


So we could imagine seeing a sequence like [z11,z12,z13,z21,z22,z31], which would repre-sent a series of noisy observations over three experimental trials.  The first is the longest,and they get shorter over the experiment.  So if we assumed noisy perceptual informationaccumulates at a rate of one sample per second, then we’d have a 3s, a 2s, and a 1s tria

```{r}
i = 1
j = 3
epsilon = 0.7
thetas = c(0.2, 0.4, 0.6, 0.8)

all_z_overbar_given_theta = c()
all_z_ij_given_theta = c()
for (theta_index in seq(1:length(thetas))){
  for (exemplar in seq(1:i)){
    for (timepoint in seq(1:j)){
     theta = thetas[theta_index]
      z_ij_given_theta = get_z_i_j_given_theta(i, j, theta, epsilon)
    all_z_ij_given_theta = c(all_z_ij_given_theta, z_ij_given_theta)
    
    }
  }
  
  z_overbar_given_theta <-  prod(all_z_ij_given_theta)
  all_z_overbar_given_theta <- c(all_z_overbar_given_theta, z_overbar_given_theta)
  
}


all_z_ij_given_theta
 # literally everything was the same?
all_z_overbar_given_theta

```

```{r}
all_z_overbar_given_theta
```

```{r}
z_overbar = sum(all_z_overbar_given_theta * thetas)
```

```{r}
posterior_distribution = (all_z_overbar_given_theta * thetas) / z_overbar
```

```{r}
posterior_distribution
```

