---
title: "02_visualization"
author: "anjie & gal"
date: "2/16/2021"
html_document:
    toc: true
    toc_float: true
    number_sections: no
---
```{r message=FALSE, warning=FALSE}

library(here)
library(tidyverse)
library(stringr) # for parsing r string 
library(jsonlite) # for parsing r string 
library(ggiraphExtra)
library(plotrix)
```

```{r read_data, message=FALSE, warning=FALSE}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))
pref_data <- read_csv(here('data/processed_data/trimmed_prefdata.csv'))
similarity_data <- read_csv(here('data/processed_data/trimmed_similaritydata.csv'))
complexity_data <- read_csv(here('data/processed_data/trimmed_complexitydata.csv'))
demog_data <- read_csv(here('data/processed_data/trimmed_demogdata.csv'))
```

# Descriptive Info 

N = 167

## sample size 

```{r}
RT_data %>% 
  distinct(subject) %>% 
  count()
```

## demographic {.tabset}

### age 

```{r}
demog_data %>% 
  ggplot(aes(x = age)) + 
  geom_histogram()
```

### ethnicity 

```{r}
demog_data %>% 
  ggplot(aes(x = ethnicity)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Gender 

```{r}
demog_data %>% 
  ggplot(aes(x = gender)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### education 
```{r}
demog_data %>% 
  ggplot(aes(x = education)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# RT raw {.tabset}

## overall 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() 
```

## by trial type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_type)
```

## by trial complexity 
```{r}
RT_data %>% 
  ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_complexity)
```

## by block type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~block_type)
```

## by item id 
### simple 
```{r}
RT_data %>% 
  filter(trial_complexity == "simple") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

### complex 
```{r}
RT_data %>% 
  filter(trial_complexity == "complex") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

# RT basic plotting 

## normal 

### separate deviant by similarity

```{r}

summarized <- RT_data %>%
group_by(trial_number, item_type, trial_complexity) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(rt), Std=sd(rt), SE = std.error(rt), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=item_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(~trial_complexity)
```
### separate by first half/second half
```{r}

summarized <- RT_data %>%
group_by(trial_number, item_type, trial_complexity, half) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(rt), Std=sd(rt), SE = std.error(rt), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=item_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(half~trial_complexity)
```

### collapsed across similar/dissimilar deviant

```{r}

summarized <- RT_data %>%
group_by(trial_number, trial_type, trial_complexity) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(rt), Std=sd(rt), SE = std.error(rt), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=trial_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(~trial_complexity)
```

## log transformed 
```{r}
summarized_log <- RT_data %>%
group_by(trial_number, item_type, trial_complexity) %>% 
summarise(meanRT=mean(log(rt)), 
          maxRT=max(log(rt)), 
          minRT=min(log(rt)), 
          medianRT=median(log(rt)), 
          Std=sd(log(rt)), 
          SE = std.error(log(rt)), 
          n = n())


ggplot(summarized_log, 
       aes(x= trial_number, y=medianRT, colour=item_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(item_type ~ trial_complexity)
```


# group all trials together
```{r}

summarized_log <- RT_data %>%
group_by(item_type, trial_complexity) %>% 
summarise(meanRT=mean((rt)), 
          maxRT=max((rt)), 
          minRT=min((rt)), 
          medianRT=median((rt)), 
          Std=sd((rt)), 
          SE = std.error((rt)), 
          n = n())

ggplot(summarized_log, 
       aes(x = item_type, y=medianRT, colour=item_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  facet_grid(~ trial_complexity)

```


# Preference test

## raw {.tabset}

### overall

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count")
  
```

### by block type 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count") + 
  facet_wrap(~block_type)
```

### by block number 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count") + 
  facet_wrap(~block_number) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## check participant pattern 
```{r}
pref_data %>% 
  group_by(subject) %>% 
  count(stim_type_selected) %>% 
  filter(stim_type_selected == "novel") %>% 
  mutate(percent_novel = n/20) %>% 
  ggplot(aes(x = percent_novel)) +
  geom_histogram(bins = 20)
```



## relationship with RT {.tabset}

### overall 
```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected, 
             y = log(trial_looking_time))) + 
  geom_point(alpha = 0.05, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") 
```

### by block type 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected, 
             y = log(trial_looking_time))) + 
  geom_point(alpha = 0.05, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot")  + 
  facet_wrap(~block_type)
```

## RT and block num {.tabset}
how long participants spent on the pref test 

### by block type 
```{r}
pref_data %>% 
  group_by(block_number, block_type) %>% 
summarise(meanRT=mean(log(trial_looking_time)), 
          maxRT=max(log(trial_looking_time)), 
          minRT=min(log(trial_looking_time)), 
          medianRT=median(log(trial_looking_time)), 
          Std=sd(log(trial_looking_time)), 
          SE = std.error(log(trial_looking_time)), 
          n = n()) %>% 
  ggplot( 
       aes(x= block_number, y=medianRT, colour=block_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Block Number") +
  facet_wrap(~block_type) 
```

### by choice 

```{r}
pref_data %>% 
  group_by(block_number, stim_type_selected) %>% 
summarise(meanRT=mean(log(trial_looking_time)), 
          maxRT=max(log(trial_looking_time)), 
          minRT=min(log(trial_looking_time)), 
          medianRT=median(log(trial_looking_time)), 
          Std=sd(log(trial_looking_time)), 
          SE = std.error(log(trial_looking_time)), 
          n = n()) %>% 
  ggplot( 
       aes(x= block_number, y=medianRT, colour=stim_type_selected)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Block Number") +
  facet_wrap(~stim_type_selected) 
```


# Similarity ratings {.tabset}

## Raw 

```{r}
similarity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)
```

## by intuitive similarity 
```{r}

similarity_data <- similarity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus_left) | grepl("complex", stimulus_right) ~ "complex", 
      grepl("simple", stimulus_right) | grepl("simple", stimulus_right) ~ "simple"
    ), 
    stimulus_left_number = as.numeric(str_extract(stimulus_left, "[[:digit:]]+")), 
    stimulus_right_number = as.numeric(str_extract(stimulus_right, "[[:digit:]]+")), 
    similarity = case_when(
      stimulus_left_number == stimulus_right_number ~ "similar", 
      TRUE ~ "dissimilar"
    )
  )

similarity_data %>% 
  ggplot(aes(x = similarity, y= rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~complexity)
```



# Complexity Ratings {.tabset}
## Raw 
```{r}
complexity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)


```

## by intuitive complexity 
```{r}
complexity_data <- complexity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus) ~ "complex", 
      grepl("simple", stimulus) ~ "simple"
    )
  )

complexity_data %>% 
  ggplot(aes(x = complexity, y = rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") 
```

