---
title: "02_visualization"
author: "anjie & gal"
date: "03/04/2021"
html_document:
    toc: true
    toc_float: true
    number_sections: no
---
```{r message=FALSE, warning=FALSE}
library(lme4)
library(here)
library(tidyverse)
library(stringr) # for parsing r string 
library(jsonlite) # for parsing r string 
library(ggiraphExtra)
library(plotrix)
library(lmerTest)

```

```{r read_data, message=FALSE, warning=FALSE}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))
#pref_data <- read_csv(here('data/processed_data/trimmed_prefdata.csv'))
similarity_data <- read_csv(here('data/processed_data/trimmed_similaritydata.csv'))
complexity_data <- read_csv(here('data/processed_data/trimmed_complexitydata.csv'))
demog_data <- read_csv(here('data/processed_data/trimmed_demogdata.csv'))
```

# Descriptive Info 

N = 402

## sample size 

```{r}
RT_data %>% 
  distinct(subject) %>% 
  count()

# reorder
RT_data$trial_complexity = factor(RT_data$trial_complexity, levels=c('simple', 'complex'))
RT_data$item_type = factor(RT_data$item_type, levels=c('background', 'similar deviant', 'dissimilar deviant'))

```

## demographic {.tabset}

### age 

```{r}
demog_data %>% 
  ggplot(aes(x = as.numeric(age))) + 
  geom_histogram()
```

### ethnicity 

```{r}
demog_data %>% 
  ggplot(aes(x = ethnicity)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Gender 

```{r}
demog_data %>% 
  ggplot(aes(x = gender)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### education 
```{r}
demog_data %>% 
  ggplot(aes(x = education)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# RT raw {.tabset}

## overall 

```{r}
RT_data %>% 
 # filter(trial_number == 1) %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
 # scale_x_log10() 
```


```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() 
```

## by trial type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_type)
```

## trial type and block 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_grid(block_type~trial_type)
```

## by trial complexity 
```{r}
RT_data %>% 
  ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_complexity)
```

## by block type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~block_type)
```



## by item id 
### simple 
```{r}
RT_data %>% 
  filter(trial_complexity == "simple") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

### complex 
```{r}
RT_data %>% 
  filter(trial_complexity == "complex") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

# Trial level RT basic plotting

## Model 
```{r}
model_log <- lmer(log(rt) ~ log(trial_number) * item_type * trial_complexity + 
                     (1 | subject), 
                   data = RT_data)

summary(model_log)$coef %>% knitr::kable(digits = 2)
```

## model with expotential fit minus the first block 
```{r}
model_log <- lmer(log(rt) ~ I((exp(1)**(-trial_number))) * item_type * trial_complexity + 
                     (1 | subject), 
                   data = RT_data)

summary(model_log)$coef %>% knitr::kable(digits = 2)
```

## block model 
```{r}
block_model_log <- lmer(log(rt) ~ log(block_number_model) *  trial_complexity + 
                     (1 | subject), 
                   data = RT_data %>% mutate(block_number_model = block_number + 1))

summary(block_model_log)$coef %>% knitr::kable(digits = 2)

block_model_exp_log <- lmer(log(rt) ~ I((exp(1)**(-block_number_model))) *  trial_complexity + 
                     (1 | subject), 
                   data = RT_data %>% mutate(block_number_model = block_number + 1))

summary(block_model_exp_log)$coef %>% knitr::kable(digits = 2)

```


## break down by block 

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x)) + 
  facet_wrap(~block_type) 
```

## break down by complexity 

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), color = trial_complexity)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x)) + 
  facet_grid(~trial_type)

```






```{r}
ggplot(RT_data, aes(x=trial_type, y=log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
  
```

```{r}
ggplot(RT_data, aes(x=trial_type_index, y=log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
  
```

## fancier version
```{r}
ggplot(RT_data, 
       aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) + 
  geom_smooth(method = "lm", 
              formula = y ~ I(exp(1)**(-x)), se = FALSE) + 
  facet_grid(half~trial_complexity) +
  langcog::scale_color_solarized(name = "Item Type") + 
  theme(legend.position = "bottom") + 
  ylab("log RT (ms)") + 
  xlab("Trial Number") 
```

```{r}
first_trial <- RT_data %>%
  filter(trial_number == 1) %>% 
  select(subject, block_number, rt) %>% 
  mutate(temp_id = paste(subject, "_", block_number)) %>% 
  mutate(rt = log(rt)) %>% 
  rename(first_trial_rt = rt) %>% 
  select(-block_number)

RT_data %>% 
  mutate(temp_id = paste(subject, "_", block_number)) %>% 
  left_join(first_trial, by = "temp_id") %>% 
  mutate(percent_rt = log(rt) / first_trial_rt) %>% 
  ggplot( 
       aes(x=trial_number, y=percent_rt, colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) + 
  geom_smooth(method = "lm", 
              formula = y ~ I(exp(1)**(-x)), se = FALSE) + 
  facet_grid(half~trial_complexity) +
  langcog::scale_color_solarized(name = "Item Type") + 
  theme(legend.position = "bottom") + 
  ylab("percent RT of first trial") + 
  xlab("Trial Number") 
```



## only look at trials before first deviant 


```{r}
RT_data %>% 
  filter(is.na(first_dev_position) | 
         trial_number < first_dev_position | 
         trial_number == first_dev_position) %>% 
  ggplot(aes(x=trial_number, y=log(rt), color = item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x)) +
  facet_wrap(~block_type)
```

```{r}
RT_data %>% 
  filter(is.na(first_dev_position) | 
         trial_number < first_dev_position | 
         trial_number == first_dev_position) %>% 
  filter(trial_number != 1) %>% 
  ggplot(aes(x=trial_number, y=log(rt), color = item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", 
               position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x)) +
  facet_wrap(~block_type) + 
  labs(title = "No first trial")
```


```{r}
ggplot(RT_data, 
       aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) + 
  geom_smooth(method = "lm", 
              formula = y ~ I(exp(1)**(-x)), se = FALSE) + 
  facet_wrap(~trial_complexity) +
  #langcog::theme_mikabr() +
  theme_classic()+
  langcog::scale_color_solarized(name = "Item Type") + 
  theme(legend.position = "bottom") + 
  ylab("log RT (seconds)") + 
  xlab("Trial Number")
sessionInfo()
```




# Block level RT basic plotting

## by block type 
```{r}

RT_data %>% 
  mutate(block_number_for_plot = block_number + 1) %>% 
ggplot(aes(x=block_number_for_plot, y=log(rt), colour=block_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_smooth(method = "lm", 
              formula = y ~ log(x))
```

## by number of deviants
```{r}

RT_data %>% 
  mutate(block_number_for_plot = block_number + 1) %>% 
ggplot(aes(x=block_number_for_plot, y=log(rt), colour=as.factor(block_deviant_number))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_smooth(method = "lm", 
              formula = y ~ log(x))
```


## by complexity
```{r}
RT_data %>% 
  mutate(block_number_for_plot = block_number + 1) %>% 
ggplot(aes(x=block_number_for_plot, 
           y=log(rt), 
           colour=trial_complexity)) + 
  scale_x_continuous(breaks = seq(1, 12, 1)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_smooth(method = "lm", 
              formula = y ~ log(x)) + 
  theme_classic()+
  xlab("Block Number")+ 
  langcog::scale_color_solarized(name = "Complexity") 
```

# Similarity ratings {.tabset}



## Raw 

```{r}
similarity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)
```

## by intuitive similarity 
```{r}

similarity_data <- similarity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus_left) | grepl("complex", stimulus_right) ~ "complex", 
      grepl("simple", stimulus_right) | grepl("simple", stimulus_right) ~ "simple"
    ), 
    stimulus_left_number = as.numeric(str_extract(stimulus_left, "[[:digit:]]+")), 
    stimulus_right_number = as.numeric(str_extract(stimulus_right, "[[:digit:]]+")), 
    similarity = case_when(
      stimulus_left_number == stimulus_right_number ~ "similar", 
      TRUE ~ "dissimilar"
    )
  )

similarity_data %>% 
  ggplot(aes(x = similarity, y= rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~complexity)
```

## Model

```{r}
similarity_rating_model_interaction <- lmer(rating~complexity*similarity + (1|subject), 
     data = similarity_data, 
     REML = FALSE)

similarity_rating_model <- lmer(rating~similarity + (1|subject), 
     data = similarity_data, 
     REML = FALSE)

anova(similarity_rating_model_interaction, similarity_rating_model)

summary(similarity_rating_model_interaction)$coef %>% knitr::kable(digits = 2)
```



# Complexity Ratings {.tabset}




## Raw 
```{r}
complexity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)


```


## by intuitive complexity 
```{r}
complexity_data <- complexity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus) ~ "complex", 
      grepl("simple", stimulus) ~ "simple"
    )
  )

complexity_data %>% 
  ggplot(aes(x = complexity, y = rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") 
```

## model 
```{r}


complexity_rating_model <- lmer(rating~complexity + (1|subject), 
     data = complexity_data)

summary(complexity_rating_model)$coef %>% knitr::kable(digits = 2)

```



## by item 
first figure out action
```{r}
complexity_action <- complexity_data %>%
  mutate(item_id_full = 
             str_match(stimulus, "spore_stims/\\s*(.*?).gif")[,2], 
         item_id_no_action = str_match(stimulus, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
         action_type = str_sub(item_id_full, -1)) 

action_summary <- complexity_action %>% 
  group_by(action_type) %>% 
  tidyboot::tidyboot_mean(rating) 

action_summary %>% 
 ggplot(aes(x = action_type, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))
```

## by complexity type 
```{r}
complexity_summary <- complexity_action %>% 
  group_by(item_id_no_action) %>% 
  tidyboot::tidyboot_mean(rating) %>% 
  mutate(
    complexity = case_when(
      grepl("complex", item_id_no_action) ~ "complex", 
      TRUE ~ "simple")
  )

complexity_summary %>% 
  ggplot(aes(x = reorder(item_id_no_action, mean), y = mean, color = complexity)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(1.5)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

# dishabituation effect 

```{r}
log_rt_deviant <- RT_data %>% 
  filter(trial_type == "deviant") %>% 
  group_by(item_id, first_dev_position) %>% 
  tidyboot::tidyboot_mean(log(rt)) %>% 
  mutate(type = "log_rt", 
    complexity = case_when(
      grepl("complex", item_id) ~ "complex", 
      TRUE ~ "simple")
  ) 

complexity_temp <- complexity_summary %>% 
  mutate(type = "rating") %>% 
  mutate(item_id = item_id_no_action) %>% 
  select(-item_id_no_action)

dishab_df <- bind_rows(log_rt_deviant, 
                       complexity_temp)
```

## raw dishabitutaiton 

```{r}
dishab_df %>% 
  ggplot(aes(x = reorder(item_id, mean), y = mean, 
             color = complexity, 
             shape = type)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(1.5)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

## effect? 
```{r}

c_temp <- complexity_temp %>% 
  select(item_id, complexity, mean) %>% 
  rename(mean_rating = mean)

log_rt_deviant %>% 
  select(item_id, mean, first_dev_position) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  facet_wrap(~ first_dev_position) +
   theme_classic() + 
  xlab("Complexity Rating") + 
  ylab("log(RT) on deviant trial") +
langcog::scale_color_solarized(name = "Item Type") 
  
```


```{r}
log_rt_deviant %>% 
  filter(complexity == "complex") %>% 
  select(item_id, mean) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

```{r}
log_rt_deviant %>% 
  filter(complexity == "simple") %>% 
  select(item_id, mean) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## first deviant only 
```{r}
log_rt_deviant <- RT_data %>% 
  filter(trial_type_index == "first_deviant") %>% 
  group_by(item_id) %>% 
  tidyboot::tidyboot_mean(log(rt)) %>% 
  mutate(type = "log_rt", 
    complexity = case_when(
      grepl("complex", item_id) ~ "complex", 
      TRUE ~ "simple")
  ) 

complexity_temp <- complexity_summary %>% 
  mutate(type = "rating") %>% 
  mutate(item_id = item_id_no_action) %>% 
  select(-item_id_no_action)

dishab_df <- bind_rows(log_rt_deviant, 
                       complexity_temp)


dishab_df %>% 
  ggplot(aes(x = reorder(item_id, mean), y = mean, 
             color = complexity, 
             shape = type)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(1.5)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) 
```

# Similarity redux 
```{r}
similarity_data %>% 
  mutate(
    stimulus_left_id =  str_match(stimulus_left, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
    stimulus_right_id = str_match(stimulus_right, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
   ) %>% 
  group_by(stimulus_left_id, similarity) %>% 
  tidyboot::tidyboot_mean(rating) %>% 
  ggplot(aes(x = reorder(stimulus_left_id, mean), y = mean, 
             color = similarity)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

# LOOK AT FIRST BLOCK 
```{r}
RT_data %>% 
  filter(block_number == 0) %>% 
  ggplot(aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
  
RT_data %>% 
  filter(block_number == 0) %>% 
  ggplot(aes(x = item_type, y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap(~block_type)



```

# LOOK AT pre-deviant and after deviant 
```{r}
block_dev_summary <- RT_data %>% 
  filter(trial_type == "deviant") %>% 
  mutate(
    block_id =  paste(subject, block_number),
    temp_dev_id = paste(trial_type, trial_number, trial_complexity)) %>% 
  select(temp_dev_id, block_id)

dev_pos_df <- RT_data %>% 
  mutate(block_id = paste(subject, block_number)) %>% 
  left_join(block_dev_summary, by = "block_id") %>% 
  separate(temp_dev_id, into = c("trial_type_temp", "deviant_pos", "deviant_complexity")) %>% 
  select(-c(block_id, trial_type)) %>% 
  rowwise() %>% 
  mutate(dishabituation_position = case_when(
    (trial_number == (as.numeric(deviant_pos)) - 1) ~ "before_deviant", 
    (trial_number == (as.numeric(deviant_pos)) + 1) ~ "after_deviant", 
    TRUE ~ "regular_deviant"
  )) %>% 
  filter(dishabituation_position != "regular_deviant" && deviant_pos != 8) 


dev_pos_df %>% 
  ggplot(aes(x = trial_number, y = log(rt), 
             color = dishabituation_position)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~deviant_complexity)

dev_pos_df %>% 
  ggplot(aes(x = trial_number, y = log(rt), 
             color = dishabituation_position)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
```


