---
title: "02_visualization"
author: "anjie & gal"
date: "2/16/2021"
html_document:
    toc: true
    toc_float: true
    number_sections: no
---
```{r message=FALSE, warning=FALSE}

library(here)
library(tidyverse)
library(stringr) # for parsing r string 
library(jsonlite) # for parsing r string 
library(ggiraphExtra)
library(plotrix)
```

```{r read_data, message=FALSE, warning=FALSE}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))
#pref_data <- read_csv(here('data/processed_data/trimmed_prefdata.csv'))
similarity_data <- read_csv(here('data/processed_data/trimmed_similaritydata.csv'))
complexity_data <- read_csv(here('data/processed_data/trimmed_complexitydata.csv'))
demog_data <- read_csv(here('data/processed_data/trimmed_demogdata.csv'))
```

# Descriptive Info 

N = 402

## sample size 

```{r}
RT_data %>% 
  distinct(subject) %>% 
  count()

# reorder
RT_data$trial_complexity = factor(RT_data$trial_complexity, levels=c('simple', 'complex'))
RT_data$item_type = factor(RT_data$item_type, levels=c('background', 'similar deviant', 'dissimilar deviant'))

```

## demographic {.tabset}

### age 

```{r}
demog_data %>% 
  ggplot(aes(x = as.numeric(age))) + 
  geom_histogram()
```

### ethnicity 

```{r}
demog_data %>% 
  ggplot(aes(x = ethnicity)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### Gender 

```{r}
demog_data %>% 
  ggplot(aes(x = gender)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

### education 
```{r}
demog_data %>% 
  ggplot(aes(x = education)) + 
  geom_histogram(stat = "count") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

# RT raw {.tabset}

## overall 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() 
```

## by trial type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_type)
```

## trial type and block 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_grid(block_type~trial_type)
```


## by trial complexity 
```{r}
RT_data %>% 
  ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~trial_complexity)
```

## by block type 
```{r}
RT_data %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~block_type)
```



## by item id 
### simple 
```{r}
RT_data %>% 
  filter(trial_complexity == "simple") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

### complex 
```{r}
RT_data %>% 
  filter(trial_complexity == "complex") %>% 
   ggplot(aes(x = rt)) + 
  geom_histogram() + 
  scale_x_log10() + 
  facet_wrap(~item_id)
```

# Trial level RT basic plotting

## trial type based

```{r}
ggplot(RT_data, aes(x=trial_type, y=log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
  
```


## trial number based  
```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), color = item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
```

## trial number based no first trial 
```{r}
RT_data %>% 
  filter(trial_number != 1) %>% 
ggplot(aes(x=trial_number, y=log(rt), color = item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type) + 
  labs(title = "No first trial")
```




## trial type based no first trial  
```{r}
RT_data %>% 
  filter(trial_number != 1) %>% 
ggplot(aes(x=trial_type, y=log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type) + 
  labs(title = "No first trial")
```

## complexity effect 
```{r}
ggplot(data = RT_data, 
       aes(x=trial_type, y=log(rt), color = trial_complexity)) + 
  stat_summary(fun.data = "mean_cl_boot") 
```


## complexity effect without the first trial 
```{r}
RT_data %>% 
  filter(trial_number != 1) %>% 
ggplot(aes(x=trial_type, y=log(rt), color = trial_complexity)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  labs(title = "No first trial")
```

## only look at the first deviant 
```{r}

```








# Block level RT basic plotting

## by block type 
```{r}
ggplot(RT_data, aes(x=block_number, y=log(rt), colour=block_type)) + 
  stat_summary(fun.data = "mean_cl_boot") 
```

## by number of deviants
```{r}
ggplot(RT_data, aes(x=block_number, y=log(rt), colour=as.factor(block_deviant_number))) + 
  stat_summary(fun.data = "mean_cl_boot") 
```




### separate deviant by similarity {.tabset}

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(half~trial_complexity) 
```


### separate by first half/second half

#### by hand 
```{r}

summarized <- RT_data %>%
group_by(trial_number, item_type, trial_complexity, half) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(log(rt)), Std=sd(rt), SE = std.error(log(rt)), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=item_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("log RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(half~trial_complexity)
```

## collapsed across similar/dissimilar deviant
=======
#### tidyboot 

```{r}
ggplot(RT_data, aes(x=trial_number, y=rt, colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(half~trial_complexity)
```

#### log transformed 
```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(half~trial_complexity)
```

```{r}
summarized <- RT_data %>%
group_by(trial_number, item_type, trial_complexity, half) %>% 
summarise(meanRT=mean(log(rt)), maxRT=max(log(rt)), minRT=min(log(rt)), medianRT=median(log(rt)), Std=sd(log(rt)), SE = std.error(log(rt)), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=item_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(half~trial_complexity)
```


### collapsed across similar/dissimilar deviant

```{r}
RT_data 
ggplot(RT_data, aes(x=trial_number, y=log(rt), color = trial_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(~trial_complexity)
```

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), color = trial_complexity)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(half~trial_type)
```



```{r}

summarized <- RT_data %>%
group_by(trial_number, trial_type, trial_complexity) %>% 
summarise(meanRT=mean(rt), maxRT=max(rt), minRT=min(rt), medianRT=median(rt), Std=sd(rt), SE = std.error(rt), n = n())


ggplot(summarized, aes(x=trial_number, y=medianRT, colour=trial_type)) + geom_line() + geom_errorbar(aes(ymin=medianRT-SE, ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + geom_line(size=1.2, position = position_dodge(width = 0.2)) + ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=22, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=17, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(~trial_complexity)
```

## log transformed 
```{r}
summarized_log <- RT_data %>%
group_by(trial_number, item_type, trial_complexity) %>% 
summarise(meanRT=mean(log(rt)), 
          maxRT=max(log(rt)), 
          minRT=min(log(rt)), 
          medianRT=median(log(rt)), 
          Std=sd(log(rt)), 
          SE = std.error(log(rt)), 
          n = n())


ggplot(summarized_log, 
       aes(x= trial_number, y=medianRT, colour=item_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Trial Number", breaks =c(2,4,6,8)) +
  facet_grid(half ~ trial_complexity)
```

## exploring function form 
```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x))+ 
  facet_grid(item_type~trial_complexity)
```

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  geom_smooth(method = "lm", 
              formula = y ~ x)+ 
  facet_grid(item_type~trial_complexity)
```

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  geom_smooth(method = "lm", 
              formula = y ~ x^2)+ 
  facet_grid(item_type~trial_complexity)
```

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  geom_smooth(method = "lm", 
              formula = y ~ x^3)+ 
  facet_grid(item_type~trial_complexity)
```



# group all trials together
```{r}

summarized_log <- RT_data %>%
group_by(item_type, trial_complexity) %>% 
summarise(meanRT=mean((rt)), 
          maxRT=max((rt)), 
          minRT=min((rt)), 
          medianRT=median((rt)), 
          Std=sd((rt)), 
          SE = std.error((rt)), 
          n = n())

ggplot(summarized_log, 
       aes(x = item_type, y=medianRT, colour=item_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("RT [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_blank(),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  facet_grid(~ trial_complexity)

```


# Preference test

## raw {.tabset}

### overall

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count")
  
```

### by block type 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count") + 
  facet_wrap(~block_type)
```

### by block number 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected)) + 
  geom_histogram(stat = "count") + 
  facet_wrap(~block_number) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## check participant pattern 
```{r}
pref_data %>% 
  group_by(subject) %>% 
  count(stim_type_selected) %>% 
  filter(stim_type_selected == "novel") %>% 
  mutate(percent_novel = n/20) %>% 
  ggplot(aes(x = percent_novel)) +
  geom_histogram(bins = 20)
```



## relationship with RT {.tabset}

### overall 
```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected, 
             y = log(trial_looking_time))) + 
  geom_point(alpha = 0.05, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") 
```

### by block type 

```{r}
pref_data %>% 
  ggplot(aes(x = stim_type_selected, 
             y = log(trial_looking_time))) + 
  geom_point(alpha = 0.05, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot")  + 
  facet_wrap(~block_type)
```

## RT and block num {.tabset}
how long participants spent on the pref test 

### by block type 
```{r}
pref_data %>% 
  group_by(block_number, block_type) %>% 
summarise(meanRT=mean(log(trial_looking_time)), 
          maxRT=max(log(trial_looking_time)), 
          minRT=min(log(trial_looking_time)), 
          medianRT=median(log(trial_looking_time)), 
          Std=sd(log(trial_looking_time)), 
          SE = std.error(log(trial_looking_time)), 
          n = n()) %>% 
  ggplot( 
       aes(x= block_number, y=medianRT, colour=block_type)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Block Number") +
  facet_wrap(~block_type) 
```

### by choice 

```{r}
pref_data %>% 
  group_by(block_number, stim_type_selected) %>% 
summarise(meanRT=mean(log(trial_looking_time)), 
          maxRT=max(log(trial_looking_time)), 
          minRT=min(log(trial_looking_time)), 
          medianRT=median(log(trial_looking_time)), 
          Std=sd(log(trial_looking_time)), 
          SE = std.error(log(trial_looking_time)), 
          n = n()) %>% 
  ggplot( 
       aes(x= block_number, y=medianRT, colour=stim_type_selected)) + 
  geom_line() + 
  geom_errorbar(aes(ymin=medianRT-SE, 
                    ymax=medianRT+SE),
                width=0.8, size = 0.8, position = position_dodge(width = 0.2), 
                show.legend = FALSE, alpha = 0.8) +
  geom_point(position = position_dodge(width = 0.2), size=2.5) + 
  geom_line(size=1.2, position = position_dodge(width = 0.2)) + 
  ylab("log(RT) [msec]") +
  theme_gray()  + theme(
    panel.grid.minor = element_blank(), 
    plot.title = element_text(hjust=0.5, size=15, face="bold"),
    axis.title.x = element_text(size=18, face='bold'),
    axis.title.y = element_text(size=18, face='bold'),
    axis.text = element_text(size=15),
    legend.title = element_blank(),
    legend.text = element_text(size=14, face='bold'),
    strip.text = element_text(size=8, face='bold'),
    legend.key.size = unit(2.5, 'lines')) + 
  scale_x_continuous(name="Block Number") +
  facet_wrap(~stim_type_selected) 
```

## preference and looking time curve 

```{r}
pref_temp <- pref_data %>% 
  mutate(temp_id = paste(subject, block_number)) %>% 
  select(temp_id, stim_type_selected)

rt_temp <- RT_data %>% 
  mutate(temp_id = paste(subject, block_number))

RT_temp_df <- left_join(pref_temp, rt_temp, by = "temp_id")

RT_temp_df %>% 
  ggplot(aes(x = trial_number, y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~stim_type_selected) 
```

```{r}

```

```{r}
RT_temp_df %>% 
  filter(!is.na(block_type)) %>% 
  ggplot(aes(x = trial_number, y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_grid(half~stim_type_selected) 
```


# Similarity ratings {.tabset}

## Raw 

```{r}
similarity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)
```

## by intuitive similarity 
```{r}

similarity_data <- similarity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus_left) | grepl("complex", stimulus_right) ~ "complex", 
      grepl("simple", stimulus_right) | grepl("simple", stimulus_right) ~ "simple"
    ), 
    stimulus_left_number = as.numeric(str_extract(stimulus_left, "[[:digit:]]+")), 
    stimulus_right_number = as.numeric(str_extract(stimulus_right, "[[:digit:]]+")), 
    similarity = case_when(
      stimulus_left_number == stimulus_right_number ~ "similar", 
      TRUE ~ "dissimilar"
    )
  )

similarity_data %>% 
  ggplot(aes(x = similarity, y= rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~complexity)
```



# Complexity Ratings {.tabset}
## Raw 
```{r}
complexity_data %>% 
  ggplot(aes(x = rating))+ 
  geom_histogram(bins = 30)


```

## by intuitive complexity 
```{r}
complexity_data <- complexity_data %>% 
  mutate(
    complexity = case_when(
      grepl("complex", stimulus) ~ "complex", 
      grepl("simple", stimulus) ~ "simple"
    )
  )

complexity_data %>% 
  ggplot(aes(x = complexity, y = rating)) + 
  geom_point(alpha = 0.1, 
             position = position_jitter(width = 0.3)) + 
   stat_summary(fun.data = "mean_cl_boot") 
```

## by item 
first figure out action
```{r}
complexity_action <- complexity_data %>%
  mutate(item_id_full = 
             str_match(stimulus, "spore_stims/\\s*(.*?).gif")[,2], 
         item_id_no_action = str_match(stimulus, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
         action_type = str_sub(item_id_full, -1)) 

action_summary <- complexity_action %>% 
  group_by(action_type) %>% 
  tidyboot::tidyboot_mean(rating) 

action_summary %>% 
 ggplot(aes(x = action_type, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))
```

## by complexity type 
```{r}
complexity_summary <- complexity_action %>% 
  group_by(item_id_no_action) %>% 
  tidyboot::tidyboot_mean(rating) %>% 
  mutate(
    complexity = case_when(
      grepl("complex", item_id_no_action) ~ "complex", 
      TRUE ~ "simple")
  )

complexity_summary %>% 
  ggplot(aes(x = reorder(item_id_no_action, mean), y = mean, color = complexity)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(1.5)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

# dishabituation effect 

```{r}
log_rt_deviant <- RT_data %>% 
  filter(trial_type == "deviant") %>% 
  group_by(item_id) %>% 
  tidyboot::tidyboot_mean(log(rt)) %>% 
  mutate(type = "log_rt", 
    complexity = case_when(
      grepl("complex", item_id) ~ "complex", 
      TRUE ~ "simple")
  ) 

complexity_temp <- complexity_summary %>% 
  mutate(type = "rating") %>% 
  mutate(item_id = item_id_no_action) %>% 
  select(-item_id_no_action)

dishab_df <- bind_rows(log_rt_deviant, 
                       complexity_temp)

dishab_df 
```

## raw dishabitutaiton 

```{r}
dishab_df %>% 
  ggplot(aes(x = reorder(item_id, mean), y = mean, 
             color = complexity, 
             shape = type)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  position = position_dodge(1.5)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

## effect? 
```{r}

c_temp <- complexity_temp %>% 
  select(item_id, complexity, mean) %>% 
  rename(mean_rating = mean)

log_rt_deviant %>% 
  select(item_id, mean) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point()
```


```{r}
log_rt_deviant %>% 
  filter(complexity == "complex") %>% 
  select(item_id, mean) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

```{r}
log_rt_deviant %>% 
  filter(complexity == "simple") %>% 
  select(item_id, mean) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

## by half 
```{r}
log_rt_deviant <- RT_data %>% 
  filter(trial_type == "deviant") %>% 
  group_by(item_id, half) %>% 
  tidyboot::tidyboot_mean(log(rt)) %>% 
  mutate(type = "log_rt", 
    complexity = case_when(
      grepl("complex", item_id) ~ "complex", 
      TRUE ~ "simple")
  ) 

complexity_temp <- complexity_summary %>% 
  mutate(type = "rating") %>% 
  mutate(item_id = item_id_no_action) %>% 
  select(-item_id_no_action)

dishab_df <- bind_rows(log_rt_deviant, 
                       complexity_temp)

dishab_df 
```

```{r}
c_temp <- complexity_temp %>% 
  select(item_id, complexity, mean) %>% 
  rename(mean_rating = mean)

log_rt_deviant %>% 
  select(item_id, mean, half) %>% 
  rename(log_mean_dishab = mean) %>% 
  left_join(c_temp, by = "item_id") %>% 
  ggplot(aes(x = mean_rating, y = log_mean_dishab, 
             color = complexity)) + 
  geom_point() + 
  facet_wrap(~half)
```

# Similarity redux 
```{r}
similarity_data %>% 
  mutate(
    stimulus_left_id =  str_match(stimulus_left, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
    stimulus_right_id = str_match(stimulus_right, "spore_stims/\\s*(.*?)..\\s*.gif")[,2],
   ) %>% 
  group_by(stimulus_left_id, similarity) %>% 
  tidyboot::tidyboot_mean(rating) %>% 
  ggplot(aes(x = reorder(stimulus_left_id, mean), y = mean, 
             color = similarity)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper)) + 
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

# try nonlinear model 
```{r}
library(mgcv)
gam_d <- RT_data %>% 
  filter(trial_type == "background") %>% 
  mutate(trial_complexity = as.factor(trial_complexity))
```

```{r}
gam_m <- gam(log(rt) ~ s(trial_number), 
             data = gam_d, 
             method = "REML")
summary(gam_m)
plot(gam_m, 
     pages = 1, 
     se = TRUE, 
     shade = TRUE)
gam.check(gam_m)
concurvity(gam_m, full = TRUE)
```

# LOOK AT FIRST BLOCK 
```{r}
RT_data %>% 
  filter(block_number == 0) %>% 
  ggplot(aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
  
RT_data %>% 
  filter(block_number == 0) %>% 
  ggplot(aes(x = item_type, y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") +
  facet_wrap(~block_type)



```

# LOOK AT pre-deviant and after deviant 
```{r}
block_dev_summary <- RT_data %>% 
  filter(trial_type == "deviant") %>% 
  mutate(
    block_id =  paste(subject, block_number),
    temp_dev_id = paste(trial_type, trial_number, trial_complexity)) %>% 
  select(temp_dev_id, block_id)

dev_pos_df <- RT_data %>% 
  mutate(block_id = paste(subject, block_number)) %>% 
  left_join(block_dev_summary, by = "block_id") %>% 
  separate(temp_dev_id, into = c("trial_type_temp", "deviant_pos", "deviant_complexity")) %>% 
  select(-c(block_id, trial_type)) %>% 
  rowwise() %>% 
  mutate(dishabituation_position = case_when(
    (trial_number == (as.numeric(deviant_pos)) - 1) ~ "before_deviant", 
    (trial_number == (as.numeric(deviant_pos)) + 1) ~ "after_deviant", 
    TRUE ~ "regular_deviant"
  )) %>% 
  filter(dishabituation_position != "regular_deviant" && deviant_pos != 8) 


dev_pos_df %>% 
  ggplot(aes(x = fct_rev(dishabituation_position), y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~deviant_complexity)

dev_pos_df %>% 
  ggplot(aes(x = fct_rev(dishabituation_position), y = log(rt))) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  facet_wrap(~block_type)
```

# Preftest Redux 
```{r}
pref_data %>% 
  group_by(block_number, stim_type_selected) %>% 
  summarise(n = n()) %>% 
  group_by(block_number) %>% 
  mutate(
    group_n = sum(n),
    percent = n/group_n
  ) %>% 
  ggplot(aes(x = block_number, y = percent, color = stim_type_selected)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```


```{r}
```

