---
title: "looking_time_modeling"
author: "anjie"
date: "3/5/2021"
html_document:
    toc: true
    toc_float: true
    number_sections: no
---
```{r message=FALSE, warning=FALSE}
library(lme4)
library(here)
library(tidyverse)
library(stringr) # for parsing r string 
library(jsonlite) # for parsing r string 
library(ggiraphExtra)
library(plotrix)
library(lmerTest)

```

```{r read_data, message=FALSE, warning=FALSE}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))
#pref_data <- read_csv(here('data/processed_data/trimmed_prefdata.csv'))
similarity_data <- read_csv(here('data/processed_data/trimmed_similaritydata.csv'))
complexity_data <- read_csv(here('data/processed_data/trimmed_complexitydata.csv'))
demog_data <- read_csv(here('data/processed_data/trimmed_demogdata.csv'))
```

# Equation 4 
> According to the hypothesis of general slowing (i.e. a single slowing coefficient), the correlation across these conditions between young and older adults' RTs should be 1, because this is simply a correlation between a variable and that same variable multiplied by a constant. 

$$ Y = mX $$


# Equation 5 
> For both name retrieval and rate of mental rotation, developmental change was well described by an exponential function of the form 

$$ Y = a + be^{ci} $$
where: 
- a represents asymptotic processing time 
- e is the base of natural logarithms 
- a + b is the intercept 
- c is the "decay" parameter that indicates how rapidly the function approaches a 
- i is age 



# Equation 6
> A simplified version of Equation 5 was used here to provide a precise characterization of change in mi as a function of age. Specifically, the predicted coefficient at maturity is 1, so Equation 5 becomes

$$m_{i} = 1 + be^{-ci}$$

where b, e, c, and i are defined as before. 

# Equation 7 

> The full and reduced data sets were also fitted to hyperbolic and power functions that have been used previoulsy to characterize nonlinear chnage. the power function was of the form 

$$m_{i} = 1 + b(i + c)^{-d} $$

# Equation 8 

> One way to summarize these results succinctly is to insert Equation 6, which provides predictions concerning change in mi with age, into Equation 4

$$Y = (1 + be^{-ci})X$$
Y is the predicted RT for youth 
X is actual RT for adults 
i is age 



```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ I((exp(1)**(-x)))) + 
  facet_grid(block_type ~ item_type) 
  
```

```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ log(x), 
              color = "black") + 
  geom_smooth(method = "lm", 
              formula = y  ~ I((exp(1)**(-x))))+
  facet_grid(block_type ~ item_type) 
```



```{r}
ggplot(RT_data, aes(x=trial_number, y=log(rt), colour=item_type)) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .1)) + 
  stat_summary(geom = "line", alpha = .5) + 
  geom_smooth(method = "lm", 
              formula = y ~ (1 +I(exp(1)**(x)))) + 
  facet_wrap(~block_type) 
```


```{r}
lm(formula = log(rt) ~ (1 + I(exp(1)^(trial_number))), 
   data = RT_data) %>% 
  summary()
```

