---
title: "RTmodels.Rmd"
author: "anjie & gal"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(lme4)
library(xtable)
library(lmerTest)
library(broom)

```

# Load data
```{r}
RT_data <- read_csv(here('data/processed_data/trimmed_RTdata.csv'))
```

# Model 

- model <- log(rt) ~ trial_number * item_type * trial_complexity + (1|subject) + (1|item)
- model <- log(rt) ~ trial_number * item_type * trial_complexity + (1|subject)
- model <- log(rt) ~ trial_number * item_type * trial_complexity + (trial_number * item_type * trial_complexity|subject)
- model <- log(rt) ~ trial_number * item_type * trial_complexity + (trial_number * item_type * trial_complexity|subject) +  (trial_number * item_type * trial_complexity|item)


starts with the third one and prune; we don't need item level: https://osf.io/zqzsu/wiki/Standard%20Analytic%20Procedures/

```{r}
model_full <- lmer('log(rt) ~ trial_number*item_type*trial_complexity  + (trial_complexity*item_type*trial_number|subject)', data=RT_data, REML=FALSE)
#boundary (singular) fit: see ?isSingular
```

```{r}
summary(model_full)
```

# pruning
```{r}
model <- lmer('log(rt) ~ trial_number*item_type*trial_complexity  + (1|subject)', data=RT_data, REML=FALSE)
summary(model)$coef %>% knitr::kable(digits = 2)
```
```{r}
model_log <- lmer(log(rt) ~ log(trial_number) * item_type * trial_complexity + 
                     (1 | subject), 
                   data = RT_data)

anova(model, model_log)
summary(model_log)$coef %>% knitr::kable(digits = 2)
```

```{r}
ggplot(filter(RT_data, item_type == "background"), 
       aes(x = trial_number, y = rt, col = trial_complexity)) + 
  geom_jitter(width = .1, alpha = .03) +
  stat_summary(geom = "line") +
  # geom_smooth(method = "lm", se = FALSE, lty = 2) + 
  scale_y_log10() + 
  scale_x_log10()
```












```{r}
broom.mixed::tidy(model) %>% 
  knitr::kable()
```

```{r}
xtable(summary(model)$coefficients)

plot(model)
qqnorm(residuals(model))
qqline(residuals(model))

```
